\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2016-11-29 Response.tex

\item \textit{The units of y axis of Figures 1 - 3 and 5 should be mentioned in the manuscript.}

The discussion of~\cref{fig:config_error} was updated to include:
\begin{correction}
    The horizontal axes of~\cref{fig:config_error} represent the domain of the spherical angles \( \lambda \) and \( \beta \) in degrees, while the vertical axes represent the unitless magnitude of the error functions defined in~\cref{eqn:psi,eqn:A,eqn:B}.    
\end{correction}

Additional detail has been added for~\cref{fig:con}:
\begin{correction}
    \Cref{fig:eR_con} shows each component of the attitude error vector,~\cref{eqn:eR}, over the simulation time span.
    \Cref{fig:Psi_con} shows the  magnitude of the combined error function,~\cref{eqn:psi}.
\end{correction}
\begin{correction}
    The angle to each of the constraints, which is measured in degrees and given by \( \arccos(r^T R^T v_i) \), is always greater than the specified angle, \( \theta_i \), in~\Cref{tab:constraints}.
\end{correction}
and some more detail for~\cref{fig:adapt}:
\begin{correction}
    \Cref{fig:Psi_adapt,fig:con_angles} are equivalent to~\cref{fig:Psi_con,fig:con_angles_con} except include the addition of the adaptive update law.
\end{correction}
\begin{correction}
    \Cref{fig:con_angles} shows that the angle, \( \arccos(r^T R^T v_i) \) and measured in degrees, between the body fixed sensor and each constraint is satisfied for the entire maneuver.
\end{correction}

Additional detail has been added for~\cref{fig:exp}:
\begin{correction}
    \Cref{fig:eR_exp} shows the behavior of each of the components of the attitude error vector, defined by~\cref{eqn:eR}, over the experiment time span.
    \Cref{fig:Psi_exp} shows the time history of the attitude error function, defined by~\cref{eqn:psi}.
    \Cref{fig:u_exp} shows the magnitude of each component of the control input in \si{\newton\meter}, which is computed from~\cref{eqn:adaptive_control}.
    Finally,~\cref{fig:con_angle_exp} shows the angle between the body-fixed sensor and the obstacle in degrees.
\end{correction}
\item \textit{Please check and correct Page 2 Line 60.}
\item \textit{The units of the parameters are missing. These should be added in the manuscript.}

### 2016-11-29 manuscript.tex
Add some additional detail for figure 5, experimental results

A sensor pointing direction is defined in the body-fixed frame of the hexrotor as \( r = [1,0,0]^T \).
We define an obstacle in the inertial frame as \( v = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}, 0]^T \) with \( \theta = \ang{12} \).
An initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d =I \).
This results in the UAV performing a \ang{90} yaw rotation about the vertical axis of the spherical joint and the constrained region is on the shortest path connecting $R_0$ and $R_d$. 
The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term and the following parameters: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\).
\begin{figure}[H]
	\centering 
    \subfigure[{Attitude error vector \(e_R\)} \label{fig:eR_exp}]{\includegraphics[width=0.5\columnwidth]{eR_exp}  }~
	\subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_exp} ]{\includegraphics[width=0.5\columnwidth]{Psi_exp} }\\
	\subfigure[{Control input \( u\) }\label{fig:u_exp}]{\includegraphics[width=0.5\columnwidth]{u_exp}  }~
	\subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.5\columnwidth]{traj_exp} }\\
    \subfigure[{Angle to constraint } \label{fig:con_angle_exp}]{\includegraphics[width=0.5\columnwidth]{figures/constraint_angles_exp.pdf} }
	\caption{Constrained Attitude stabilization experiment}
	\label{fig:exp} 
\end{figure}
The experimental results are shown in~\Cref{fig:exp}.
In order to maneuver the system ``close" to the constrained zone we utilize several intermediary set points on either side of the obstacle.
From the initial attitude the hexrotor rotates to the first set point, pauses, and then continues around the obstacle to the second set point before continuing toward the desired attitude.
As a result this creates the stepped behavior of the configuration error history as shown in~\cref{fig:Psi_exp}.

>>>>

A sensor pointing direction is defined in the body-fixed frame of the hexrotor as \( r = [1,0,0]^T \).
We define an obstacle in the inertial frame as \( v = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}, 0]^T \) with \( \theta = \ang{12} \).
An initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d =I \).
This results in the UAV performing a \ang{90} yaw rotation about the vertical axis of the spherical joint and the constrained region is on the shortest path connecting $R_0$ and $R_d$. 
The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term and the following parameters: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\).
\begin{figure}[H]
	\centering 
    \subfigure[{Attitude error vector \(e_R\)} \label{fig:eR_exp}]{\includegraphics[width=0.5\columnwidth]{eR_exp}  }~
	\subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_exp} ]{\includegraphics[width=0.5\columnwidth]{Psi_exp} }\\
	\subfigure[{Control input \( u\) }\label{fig:u_exp}]{\includegraphics[width=0.5\columnwidth]{u_exp}  }~
	\subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.5\columnwidth]{traj_exp} }\\
    \subfigure[{Angle to constraint } \label{fig:con_angle_exp}]{\includegraphics[width=0.5\columnwidth]{figures/constraint_angles_exp.pdf} }
	\caption{Constrained Attitude stabilization experiment}
	\label{fig:exp} 
\end{figure}
The experimental results are shown in~\Cref{fig:exp}.
\Cref{fig:eR_exp} shows the behavior of each of the components of the attitude error vector, defined by~\cref{eqn:eR}, over the experiment time span.
\Cref{fig:Psi_exp} shows the time history of the attitude error function, defined by~\cref{eqn:psi}.
\Cref{fig:u_exp} shows the magnitude of each component of the control input in \si{\newton\meter}, which is computed from~\cref{eqn:adaptive_control}.
Finally,~\cref{fig:con_angle_exp} shows the angle between the body-fixed sensor and the obstacle in degrees.
In order to maneuver the system ``close" to the constrained zone we utilize several intermediary set points on either side of the obstacle.
From the initial attitude the hexrotor rotates to the first set point, pauses, and then continues around the obstacle to the second set point before continuing toward the desired attitude.
As a result this creates the stepped behavior of the configuration error history as shown in~\cref{fig:Psi_exp}.
